-----------------------------------------
title: "Rio Tinto"
author: "Amir Amin"
date: "01 October 2019"
Project: Power Consumption Prediction
output: html_document
-----------------------------------------
Pre-processing
-----------------------------------------

# import the packages
Install the packages (*** run this part just if you don't have these packages on your PC)
```{r}
# install.packages(c("corrplot","mlbench","caret", 
#                    "mice","VIM","readr",
#                    "gganimate","tseries","scales", 
#                    "ggplot2","dplyr","rmarkdown",
#                    "tidyr","lubridate","labeling", 
#                    "forecast","gapminder", 
#                    "gifski","transformr"))
```


call the packages
```{r}
library(corrplot) # plot the correlation
library(mlbench) # remove strongly correlated features
library(caret) # ML algorithms
library(mice) # Handlinf missed data
library(VIM) # plot missing values
library("readr") # save the dataset
library(gganimate)
library(tseries)
library(scales)

library(ggplot2)
library(dplyr)
library(rmarkdown)
library(tidyr)
library(lubridate)
library(labeling)
library(forecast)

library(gapminder)
library(gifski)
library(transformr)

# make sure that you have installed all of these packages
```


# import the dataset
```{r}
setwd("C:/Users/AMI017/Desktop/Rio")
power_data <- read.csv("Book_1.csv", header = TRUE)
```


# undertand the data
1- see the name of features
```{r}
colnames(power_data)
```


2- dimension of dataset & few values of features
```{r}
dim(power_data)
head(power_data, n = 5) # top 5 rows
```


3- split date and time
```{r}
myDate <- as.Date(power_data$date) #already got this one from the answers above
myTime <- format(as.POSIXct(power_data$date) ,format = "%H:%M")
myTime <- myTime[ order(myTime , decreasing = FALSE )]
```


4- merge separated date and time to the main dataset
```{r}
power_data <- cbind(power_data, myDate, myTime)
```


5- change the format of date
```{r}
power_data$myDate <- as.Date(power_data$myDate, "%d/%m/%Y") 
```


6- specify weekdays
```{r}
myWeek <- weekdays(as.Date(power_data$myDate,format="%m/%d/%Y"))
```


7- specify the months 
```{r}
myMonth <- months(power_data$myDate)
```


8- merge weekdays and months to the main dataset
```{r}
power_data <- cbind(power_data, myWeek, myMonth)
```


9- sort the months
```{r}
power_data$myMonth <- ordered(power_data$myMonth, month.name)
```


10- Monthly power consumption (it's important because customers pay monthly)
```{r}
ggplot(power_data, aes(x = myMonth, fill = myMonth))+
  geom_bar(aes(y = Appliances / 1000), stat="identity") +
  xlab("") +
  ylab("Total Power Consumption (KW)") +
  labs(fill = " ") +
  theme(legend.position = "right", 
            legend.text=element_text(size=10),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=10, angle=0, hjust= 0.5, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=10, angle=0), 
            axis.title.x = element_text(face="bold", vjust=0, size=10),  # X axis title
            axis.title.y = element_text(face="bold", hjust= 0.5, vjust= 3 , size=10))

ggsave("monthly_power_consumption.png")

```


monthly power consumption (animation)
```{r}
monthly_power <- ggplot(power_data, aes(x = myMonth, fill = myMonth))+
  geom_bar(aes(y = Appliances / 1000), stat="identity") +
  xlab("") +
  ylab("Total Power Consumption (KW)") +
  labs(fill = " ") +
  theme(legend.position = "right", 
            legend.text=element_text(size=16, color="#993333",face="bold"),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=16, angle=45, hjust= 1, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=16, angle=0), 
            axis.title.x = element_text(face="bold",color="#993333", vjust=0, size=16),  # X axis title
            axis.title.y = element_text(face="bold",color="#993333", hjust= 0.5, vjust= 3 , size=16),
            plot.title = element_text(size = 30, face = "bold", colour = "red")
            ) +
  transition_states(as.Date(power_data$date), wrap = TRUE, transition_length = 0.1, state_length = 0.1) +
  shadow_mark() +
  labs(title = '{closest_state}')

animate(monthly_power, fps = 15, duration = 20, height = 600, width =600)
anim_save("monthly_power_consumption.gif")
```


11- Weekdays power consumption
```{r}
ggplot(power_data, aes(x = factor(myWeek, weekdays(min(power_data$myDate) + 0:6)) , y = Appliances, fill = myMonth)) +
  geom_bar(stat="identity", position =  position_dodge()) +
  xlab("") +
  ylab("Power Consumption (W)") +
  labs(fill = " ") +
  theme(legend.position = "right", 
            legend.text=element_text(size=10),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=10, angle=30, hjust= 0.75, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=10, angle=0), 
            axis.title.x = element_text(face="bold", vjust=0, size=10),  # X axis title
            axis.title.y = element_text(face="bold", hjust= 0.5, vjust= 3 , size=10))
ggsave("weekdays_power_consumption.png")
```


Weekdays power consumption (animation)
```{r}
weekly_power <- ggplot(power_data, aes(x = factor(myWeek, weekdays(min(power_data$myDate) + 0:6)) , y = Appliances, fill = myMonth)) +
  geom_bar(stat="identity", position =  position_dodge()) +
  xlab("") +
  ylab("Power Consumption (W)") +
  labs(fill = " ") + 
  theme(legend.position = "right", 
            legend.text=element_text(size=16, color="#993333",face="bold"),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=16, angle=45, hjust= 1, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=16, angle=0), 
            axis.title.x = element_text(face="bold",color="#993333", vjust=0, size=16),  # X axis title
            axis.title.y = element_text(face="bold",color="#993333", hjust= 0.5, vjust= 3 , size=16),
            plot.title = element_text(size = 30, face = "bold", colour = "red")
            ) +
  transition_states(as.Date(power_data$date), wrap = TRUE, transition_length = 1, state_length = 1) +
  shadow_mark() +
  labs(title = 'Date: {closest_state}')

animate(weekly_power, fps = 20, duration = 30, height = 600, width =600)
anim_save("weekdays_power_consumption.gif")
```


12- Detailed daily power consumption
```{r}
# power_data$date <- as.Date(power_data$date)

ggplot(power_data, aes(x = unique(as.POSIXct(date)), colour = myMonth)) +
    geom_point(aes(y = Appliances)) +
    xlab("") +
    ylab("Power Consumption (W)") +
    labs(colour = " ") +
    scale_x_datetime( breaks = date_breaks("1 week"),
                      labels = date_format("%a-%d- %m", tz="CET"),
                      expand = c(0,0)) +
    theme(legend.position = "right", 
            legend.text=element_text(size=10),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=10, angle=45, hjust= 1, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=10, angle=0), 
            axis.title.x = element_text(face="bold", vjust=0, size=10),  # X axis title
            axis.title.y = element_text(face="bold", hjust= 0.5, vjust= 3 , size=10)) 
ggsave("daily_power_consumption.png")

```


Detailed daily power consumption (animation)
```{r}
daily_power <- ggplot(power_data, aes(x = unique(as.POSIXct(date)), colour = myMonth)) +
    geom_point(aes(y = Appliances)) +
    xlab("") +
    ylab("Power Consumption (W)") +
    labs(colour = " ") +
    scale_x_datetime( breaks = date_breaks("1 week"),
                      labels = date_format("%a-%d- %m", tz="CET"),
                      expand = c(0,0)) +
    theme(legend.position = "right", 
            legend.text=element_text(size=16, color="#993333",face="bold"),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=16, angle=45, hjust= 1, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=16, angle=0), 
            axis.title.x = element_text(face="bold",color="#993333", vjust=0, size=16),  # X axis title
            axis.title.y = element_text(face="bold",color="#993333", hjust= 0.5, vjust= 3 , size=16),
            plot.title = element_text(size = 30, face = "bold", colour = "red")
            )  +
  transition_states(as.Date(power_data$date), wrap = TRUE, transition_length = 1, state_length = 1) +
  shadow_mark() +
  labs(title = 'Date: {closest_state}')

animate(daily_power, fps = 20, duration = 30, height = 600, width =600)
anim_save("daily_power_consumption.gif")
```


# Understanding each of the features and their importance
13- histogram of the features (frequency of data)
```{r}
for (i in 2:dim(power_data)[2]) { # Hist
  hist(power_data[,i], xlab = colnames(power_data[i]), col = "red", main= "")$breaks
  summary(power_data[,i])
}
```


14- boxplot of features (range of data)
```{r}
#par(mfrow = c (5,6))
for (i in 2:dim(power_data)[2]) { # Boxplot
  boxplot(power_data[,i], outcol = "red", outcex = 1.5, ylab = colnames(power_data[i]))
}
```
- T1 to T9, except T6, have the same range
- RH1-1 to RH-9, except RH-6, have the same range
- T6 and Tout, rv1 and rv2, have also the same range


15- Distribution of features (changes of each feature)
```{r}
# par(mfrow = c (5,6))
for (i in 5:dim(power_data)[2]) { # Disctribution of data
  plot(power_data[,i], col = "red", ylab = colnames(power_data[i]), xlab = "")
}

```


16- Correlation between the features
```{r}
# See the correlation
corr_value <- cor(power_data[,c(2:29)], 
                  use = "pairwise.complete.obs") # Correlation 

# par(mfrow = c (1,1)) # to see the fig bigger
png(height=1200, width=1200, pointsize=25, file="Correlation.png")

corrplot(corr_value, 
         method="pie",  
         type = "upper",
         tl.col = "black",
         tl.srt = 90, 
         sig.level = 0.01, 
         insig = "blank",
         tl.cex = 0.7) 

```
- internal temperatures (except T6) are strongly correlated
- internal humidity (except RH-6) are strongly correlated
- rv1 and rv2 are strongly correlated
- T6 is the outdoor sensor since its values are similar to the outdoor values


# manage the missing values
- 1- percentage of NA values for each feature (in each column and row)
```{r}
sum(is.na(power_data))# 78667 NA values

pMiss <- function(x){sum(is.na(x))/length(x)*100}
apply(power_data,2,pMiss)# Check each column
apply(power_data,1,pMiss)# Check each row
```


2- pattern of the missing data (pattern can be seen in high resolutionn PC)
```{r}
aggr_plot <- aggr(power_data, 
                  col=c('navyblue','red'), 
                  numbers=TRUE, 
                  sortVars=TRUE, 
                  labels=names(data), 
                  cex.axis=.7, 
                  gap=3, 
                  ylab=c("Histogram of missing data","Pattern"))
```


3- predict the NA values based on the values of the rest of data using Random Forest technique
```{r}
predicted_NA_values <- mice(power_data[,2:dim(power_data)[2]],
                 m=5,
                 maxit=5,
                 meth='pmm',
                 seed=500)
```


4- summary of predicted values
```{r}
summary(predicted_NA_values)
```


5- impute the missing data using mice
```{r}
# NA values were in columns 2 to 29
# replace them with their predicted values
completedData <- mice::complete(predicted_NA_values,1)
power_data[,2:dim(power_data)[2]] <- completedData
```


6- check whether there is still any NA data in the dataset
```{r}
sum(is.na(power_data))
```
- no NA data left


7- boxplot of the features to compare their values before and after imputing NA data
```{r}
for (i in 2:dim(power_data)[2]) { # Hist
  boxplot(power_data[,i], outcol = "red", outcex = 1.5, main = colnames(power_data[i]))
  summary(power_data[,i])
}
```
Tout and T6 are almost the same; T6 should be for outdoor area (Alfresco or balcony).


# save the new dataset without any NA values
dataset is ready to be used to develop the predictive algorithm
```{r}
write_csv(power_data,"C:/Users/AMI017/Desktop/Rio/power_data.csv")
# View(head(power_consumption))
```


# Question-1: T6 is really outdoor tempearture?
Average of indoor temperature (T6 excluded)
```{r}
sum_temp <- 0
for (i in c("T1","T2","T3","T4","T5","T7","T8","T9")) {
  sum_temp <- sum_temp + power_data[,i]
}
avg_indoor_temp <- sum_temp / 8
```


plot the temperature range
```{r}
boxplot(cbind(power_data[,c("T1","T2","T3","T4","T5","T6","T7","T8","T9","T_out")]),
# boxplot(cbind(power_data[,c("T1","T2","T3","T4","T5","T6","T7","T8","T9","T_out")], Tav = avg_indoor_temp),
        outcol = "red", outcex = 1.5)
grid(NA, 5, lwd = 2)
grid (NULL,NULL, lty = 10, col = "cornsilk2")
```
- T6 range is similar to Tout
- So, for internal tempearture,we should exclude T6


# Question-2: how's humity of internal areas?
Average of input humidity (RH_6 excluded)
```{r}
sum_humidity <- 0
for (i in c("RH_1","RH_2","RH_3","RH_4","RH_5","RH_7","RH_8","RH_9")) {
  sum_humidity <- sum_humidity + power_data[,i]
}
avg_indoor_humidity <- sum_humidity / 8
```


humidity range
```{r}
boxplot(cbind(power_data[,c("RH_1","RH_2","RH_3","RH_4","RH_5","RH_6","RH_7","RH_8","RH_9","RH_out")],
              avg_indoor_humidity),
        outcol = "red", outcex = 1.5)
grid(NA, 5, lwd = 2)
grid (NULL,NULL, lty = 10, col = "cornsilk2")
```


# Question-3: how are the rest of features (columns 23-28)?
```{r}
boxplot(power_data[23:29])
```
- rv1 and rv2 are strongy related and show almost the same values


we consider the average of rv1 and rv2 since they show almost similar data
```{r}
avg_rv <- (power_data[,c("rv1")] + power_data[,c("rv2")])/2
```


- Now we have 1 value for internal temperature, 1 for internal humidity, and 1 for rv
- To understand how the power consumption changes at home, Temperature and humidity difference is important (not their specific values)
```{r}
temp_difference <- avg_indoor_temp - power_data[,c("T_out")]
humidity_difference <- avg_indoor_humidity - power_data[,c("RH_out")]
```


# focus on the final features 
we call the new dataset "power_consumption"
```{r}
power_consumption <- data.frame(power_data[,c("date","Appliances","lights")],
                                temp_difference,
                                humidity_difference,
                                power_data[,c("Press_mm_hg","Windspeed","Visibility","Tdewpoint")],
                                avg_rv) # main dataset
```


# manage outliers of inputs
```{r}
# although we see outliers on the boxplot, values are not unrealistic
# So, we can't remove the outliers because they are in the normal range
```



# handle outliers
```{r}
# counter <- 0 # count the number of outliers
# limited_max <- double(dim(power_consumption)[2]-3)
# limited_min <- double(dim(power_consumption)[2]-3)
# outlier_cutoff_1 <- double(dim(power_consumption)[2]-3)
# outlier_cutoff_2 <- double(dim(power_consumption)[2]-3)
# 
# # Find max and min of each column just cthe data inside the boundary (not outliers)
# for (i in 4:dim(power_consumption)[2]) {
#   outlier_cutoff_1[i] <- quantile(power_consumption[,i],0.75, na.rm = TRUE) + 1.5 * IQR(power_consumption[,i], na.rm = TRUE)
#   outlier_cutoff_2[i] <- quantile(power_consumption[,i],0.25, na.rm = TRUE) - 1.5 * IQR(power_consumption[,i], na.rm = TRUE)
#   # Interquartile Range (IQR) = Q3 - Q1
#   
#   limited_max[i] <- max(power_consumption[which(power_consumption[,i] < outlier_cutoff_1[i] & power_consumption[,i] > outlier_cutoff_2[i]),i])
#   limited_min[i] <- min(power_consumption[which(power_consumption[,i] < outlier_cutoff_1[i] & power_consumption[,i] > outlier_cutoff_2[i]),i])
# }
# 
# # Replace outliers with min/max of each column
# # We tried 2 methods: 1- replace with 0.5 and 0.95 quantiles (still had outlier), 
# # 2- min-max of data inside boundry (2 didnt have outlier and better)
# for (i in 4:dim(power_consumption)[2]) { # 4 different approches to handle outliers 
#   print(colnames(power_consumption[i]))
# 
#   # caps <- quantile(power_consumption[,i], probs=c(.05, .95), na.rm = T)
#   for (j in 1:dim(power_consumption)[1]) { # row
#     if(!is.na(power_consumption[j,i])){
#       if((power_consumption[j,i] > outlier_cutoff_1[i])){
#         counter <- counter + 1
#         #power_consumption[j,i] <- caps[2] # Replace outlier with mean value
#         power_consumption[j,i] <- limited_max[i] # Replace outlier with max value
#       } 
#       else if(power_consumption[j,i] < outlier_cutoff_2[i]){
#         counter <- counter + 1
#         #power_consumption[j,i] <- caps[1] # Replace outlier with min value
#         power_consumption[j,i] <- limited_min[i]
#       }
#     }
#   }
#   print(counter)
#   counter <- 0
# }
# 
# for (i in 4:dim(power_consumption)[2]) { 
#   boxplot(power_consumption[,i], outcol = "red", outcex = 1.5, ylab = colnames(power_consumption[i]))
# }
```


# feature selection
- which features are strongly correlated?
```{r}
corr_value <- cor(power_consumption[,2:dim(power_consumption)[2]])
corrplot(corr_value, 
         method="pie", 
         type = "upper", 
         order = "alphabet",
         tl.col = "black", 
         tl.srt = 45, 
         sig.level = 0.01, 
         insig = "blank")

# we consider 70% correlation as the strong correlation
highly_Correlated <- findCorrelation(corr_value, cutoff=0.7) 
print(colnames(power_consumption[,2:dim(power_consumption)[2]][highly_Correlated])) 

# temp_difference and Tdewpoint are strongly correlated
# so, we exclude Tdewpoint because we can find its value using the temp_difference values
which(colnames(power_consumption)=="Tdewpoint") # Tdewpoint is column 11
```


- Remove strongly correlated features
```{r}
power_consumption  <- power_consumption[,-c(9)] # "Tdewpoint" is excluded
```


# save the pre-processed dataset
dataset is ready to be used to develop the predictive algorithm
```{r}
write_csv(power_consumption,"C:/Users/AMI017/Desktop/Rio/power_consumption.csv")
# View(head(power_consumption))
```


# import our prepared dataset without any NA
```{r}
power_consumption <- read.csv("power_consumption.csv")
```


split date and time in the new dataset
```{r}
myDate <- as.Date(power_consumption$date) #already got this one from the answers above
myTime <- format(as.POSIXct(power_consumption$date) ,format = "%H:%M")
myTime <- myTime[ order(myTime , decreasing = FALSE )]
power_consumption <- cbind(power_consumption, myDate, myTime)
power_consumption$myDate <- as.Date(power_consumption$myDate, "%d/%m/%Y") 
myWeek <- weekdays(as.Date(power_consumption$myDate,format="%m/%d/%Y"))
myMonth <- months(power_consumption$myDate)
power_consumption <- cbind(power_consumption, myWeek, myMonth)
power_consumption$myMonth <- ordered(power_consumption$myMonth, month.name)

```


consider total power consumption and average of weather condition each day
```{r}
temp_avg <- double(0)
humidity_avg <- double(0)
pressure_avg <- double(0)
wind_avg <- double(0)
visibility_avg <- double(0)
rv_avg <- double(0)
Appliances_total <- double(0)
lights_total <- double(0)
c <- 0 # counter

for (i in unique(power_consumption$myDate)) {
  c <- c + 1
  
  temp_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'temp_difference']) 
  humidity_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'humidity_difference'])
  pressure_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'Press_mm_hg']) 
  wind_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'Windspeed']) 
  visibility_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'Visibility']) 
  rv_avg[c] <- mean(power_consumption[which(power_consumption$myDate == i),'avg_rv']) 
  Appliances_total[c] <- sum(power_consumption[which(power_consumption$myDate == i),'Appliances']) 
  lights_total[c] <- sum(power_consumption[which(power_consumption$myDate == i),'lights']) 
}
```


days of collected data
```{r}
length(unique(power_consumption$myDate)) # 138 days data
```



```{r}
daily_dataset <- data.frame(
                             date = unique(power_consumption$myDate),
                             temp = temp_avg,
                             humidity = humidity_avg,
                             press = pressure_avg,
                             wind = wind_avg,
                             visib = visibility_avg,
                             rv = rv_avg,
                             Appliances = Appliances_total,
                             lights = lights_total)

write_csv(daily_dataset,"C:/Users/AMI017/Desktop/Rio/daily_dataset.csv")
daily_dataset <- cbind(daily_dataset, month = months(daily_dataset$date))
daily_dataset$month <- ordered(daily_dataset$month, month.name)

```



total power consumed everyday
```{r}
ggplot(daily_dataset, aes(date, Appliances / 1000, fill = month)) +
  geom_bar(stat="identity", position =  position_dodge()) +
  xlab("") +
  ylab("Total Power Consumption Per Day (KW)") +
  labs(fill = " ") +
  theme(legend.position = "top", 
              legend.text=element_text(size=10),
              legend.box = "vertical",
              axis.text.x = element_text(face="bold",color="#993333", size=-10, angle=0, hjust= -2, vjust = 0), # x , y labels
              axis.text.y = element_text(face="bold",color="#993333", size=10, angle=0), 
              axis.title.x = element_text(face="bold", vjust=0, size=10),  # X axis title
              axis.title.y = element_text(face="bold", hjust= 0.5, vjust= 3 , size=10)) 

ggsave("total_daily_power_consumption.png")
```



total power consumed everyday (animation)
```{r}
total_daily <- ggplot(daily_dataset, aes(date, Appliances / 1000, fill = month)) +
  geom_bar(stat="identity", position =  position_dodge()) +
  xlab("") +
  ylab("Total Power Consumption Per Day (KW)") +
  labs(fill = " ") + 
  theme(legend.position = "right", 
            legend.text=element_text(size=16, color="#993333",face="bold"),
            legend.box = "vertical",
            axis.text.x = element_text(face="bold",color="#993333", size=16, angle=45, hjust= 1, vjust = 1), # x , y labels
            axis.text.y = element_text(face="bold",color="#993333", size=16, angle=0), 
            axis.title.x = element_text(face="bold",color="#993333", vjust=0, size=16),  # X axis title
            axis.title.y = element_text(face="bold",color="#993333", hjust= 0.5, vjust= 3 , size=16),
            plot.title = element_text(size = 30, face = "bold", colour = "red")
            )  +
  transition_states(date, wrap = TRUE, transition_length = 1, state_length = 1) +
  shadow_mark() +
  labs(title = 'Date: {closest_state}')

animate(total_daily, fps = 20, duration = 18, height = 600, width =600)
anim_save("total_daily_power_consumption_power_consumption.gif")

```



# Normalise inputs
- see the range of inputs before normalisation (columns 4-9)
```{r}
boxplot(daily_dataset[,2:7], outcol = "red", outcex = 1.5)
```
- features have different range; so we need normalisation

```{r}
colnames(daily_dataset)
```



- Z-score normalization
```{r}
sd_value <- double(6) # columns 1-3 are not input
mean_value <- double(6)

for (i in 2:7) {
  sd_value[i] <- sd(daily_dataset[,i], na.rm = TRUE)
  mean_value[i] <- mean(daily_dataset[,i], na.rm = TRUE)
  daily_dataset[,i] <- (daily_dataset[,i]- mean_value[i])/ sd_value[i] # standardise the data
}
```


- see the normalised features and check their range
```{r}
boxplot(daily_dataset[,2:7], outcol = "red", outcex = 1.5)
```
*** Now data is ready to be used to develop a predictive model

```{r}
write_csv(daily_dataset,"C:/Users/AMI017/Desktop/Rio/daily_dataset_normalised.csv")
```
